The Ranked Nearest Neighbour Interchange space

### 2019-06-13 paper.tex
minor

    Step($k \to k+1$):
    Let $T_1$ and $T_2$ be trees on $n+1$ taxa with distance $d(T_1,T_2) = k$.
    Let $T_2'$ be the last tree on a shortest path from $T_1$ to $T_2$, i.e. $d(T_1,T_2') = k$.
    We can apply the induction hypothesis on $T_1$ and $T_2'$ and see that $d(T_1|_n, T_2'|_n) \leq d(T_1, T_2') - |r_{T_1}(p_{n+1}) - r_{T_2'}(p_{n+1})| := k - m$.
    Now we differ two cases:
    \begin{enumerate}
        \item $p_{n+1}$ changes its rank between $T_2$ and $T_2'$.

        Then the trees $T_2|_n$ and $T_2'|_n$ are equal. \todo{Is this obivous?}
        Therefore, it is $d(T_1|_n,T_2|_n) = d(T_1|_n, T_2'|_n) \leq k - m$.
        Since the rank of $p_{n+1}$ changes by one between $T_2$ and $T_2'$ it is either $|r_{T_1}(p_{n+1}) - r_{T_2}(p_{n+1})| = m+1$ or $|r_{T_1}(p_{n+1}) - r_{T_2}(p_{n+1})| = m-1$.
        In either case, we have $d(T_1|_n,T_2|_n) = d(T_1|_n, T_2'|_n) \leq k - m = (k+1) - (m-1) \leq d(T_1, T_2) - |r_{T_1}(p_{n+1}) - r_{T_2}(p_{n+1})|$.

>>>>

    Step($k \to k+1$):
    Let $T_1$ and $T_2$ be trees on $n+1$ taxa with distance $d(T_1,T_2) = k$.
    Let $T_2'$ be the last tree on a shortest path from $T_1$ to $T_2$, i.e. $d(T_1,T_2') = k$.
    We can apply the induction hypothesis on $T_1$ and $T_2'$ and see that $d(T_1|_n, T_2'|_n) \leq d(T_1, T_2') - |r_{T_1}(p_{n+1}) - r_{T_2'}(p_{n+1})| := k - m$.
    Now we differ two cases:
    \begin{enumerate}
        \item $p_{n+1}$ changes its rank between $T_2$ and $T_2'$ or is affected by the $\nni$ move is performed between $T_2$ and $T_2'$.

        Then the trees $T_2|_n$ and $T_2'|_n$ are equal. \todo{Is this obivous?}
        Therefore, it is $d(T_1|_n,T_2|_n) = d(T_1|_n, T_2'|_n) \leq k - m$.
        It is either $|r_{T_1}(p_{n+1}) - r_{T_2}(p_{n+1})| = m+1$, $|r_{T_1}(p_{n+1}) - r_{T_2}(p_{n+1})| = m$, or $|r_{T_1}(p_{n+1}) - r_{T_2}(p_{n+1})| = m-1$.
        In either case, we have $d(T_1|_n,T_2|_n) = d(T_1|_n, T_2'|_n) \leq k - m = (k+1) - (m+1) \leq d(T_1, T_2) - |r_{T_1}(p_{n+1}) - r_{T_2}(p_{n+1})|$.
